A Particle Swarm Optimisation-Based Indirect Approach to Web Service Composition

### 2015-10-13 paper.tex
Finished writing pseudocode algorithms.

\begin{algorithm}
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$I$, $O$, $R$}
 \Output{a list of services $S_{list}$}
 $C_{search} \leftarrow I$\;
 $S_{list} \leftarrow \{\}$\;
 $S_{found} \leftarrow DiscoverService()$\;
 \While{$|S_{found}| > 0$}{
  $S_{list} \leftarrow S_{list} \cup S_{found}$\;
  $C_{search} \leftarrow C_{search} \cup C_{output}$ of $S_{found}$\;
  $S_{found} \leftarrow DiscoverService()$\;
  }
  \eIf{$C_{search} \supseteq O$}{
   \Return $S_{list}$\;
   }{
   Report no solution\;
 }
\caption{Discovering relevant services for compositio and tracking composition layers.}
\label{layeredDiscovery}
\end{algorithm}

@@

@@

>>>>

\begin{algorithm}
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$I$, $O$, $R$}
 \Output{a list of services $S_{list}$}
 $C_{search} \leftarrow I$\;
 $S_{list} \leftarrow \{\}$\;
 $S_{found} \leftarrow DiscoverService()$\;
 \While{$|S_{found}| > 0$}{
  $S_{list} \leftarrow S_{list} \cup S_{found}$\;
  $C_{search} \leftarrow C_{search} \cup C_{output}$ of $S_{found}$\;
  $S_{found} \leftarrow DiscoverService()$\;
  }
  \eIf{$C_{search} \supseteq O$}{
   \Return $S_{list}$\;
   }{
   Report no solution\;
 }
\caption{Discovering relevant services for composition and tracking composition layers.}
\label{layeredDiscovery}
\end{algorithm}

@@

\begin{algorithm}
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{filterByLayer}{filterByLayer}\SetKwFunction{mergeLayers}{mergeLayers}\SetKwFunction{findHighestTime}{findHighestTime}
 \SetKwFunction{eNull}{null}\SetKwFunction{getInputsSatisfied}{getInputsSatisfied}\SetKwFunction{calculateFitness}{calculateFitness}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$end$, sorted layers $L$}
 \Output{fitness $f$}
 $solution \leftarrow \{\}$\;
 $cost \leftarrow 0$\;
 $availability \leftarrow 1$\;
 $reliability \leftarrow 1$\;
 $nextToSatisfy \leftarrow \{\}$\;
 \ForAll{$inputs$ of $end$}{
    $nextToSatisfy \leftarrow nextToSatisfy \cup \{(input, end.time, |L|)\}$\;
 }
 $i \leftarrow |L|$\;
 \For{$i=|L|$ to $i=1$}{
    $toSatisfy \leftarrow \filterByLayer(nextToSatisfy,i)$\;
    $nextToSatisfy \leftarrow nextToSatisfy - toSatisfy$\;
    $mergedL \leftarrow \mergeLayers(L,i)$\;
    \While{$|toSatisfy| > 0$}{
	$nextS \leftarrow mergedL.next()$\;
	\eIf{$nextS = \eNull$}{
	    $nextToSatisfy \leftarrow nextToSatisfy \cup toSatisfy$\;
	    $toSatisfy \leftarrow \{\}$\;
	}{
	    $nLayer \leftarrow nextS.layer$\;
	    $satisfied \leftarrow \getInputsSatisfied(toSatisfy,nextS)$\;
	    \If{$|satisfied| > 0$}{
		$solution \leftarrow solution \cup \{nextS\}$\;
		$cost \leftarrow cost + nextS.QoS.time$\;
		$availability \leftarrow availability \times nextS.QoS.availability$\;
		$reliability \leftarrow reliability \times nextS.QoS.reliability$\;
	    }
	    $time \leftarrow nextS.QoS.time$\;
	    $toSatisfy \leftarrow toSatisfy - satisfied$\;
	    $highestTime \leftarrow \findHighestTime(satisfied)$\;
	    \ForAll{$inputs$ of $nextS$}{
		$nextToSatisfy \leftarrow nextToSatisfy \cup \{(input, time + highestTime, nLayer)\}$\;
	    }
	}
    }
 }
 $time \leftarrow \findHighestTime(nextToSatisfy)$\;
 $f \leftarrow \calculateFitness(cost,time,availability,reliability)$\;
 \Return $f$\;
\caption{Algorithm for decoding solutions and calculating their fitness.}
\label{solutionDecoding}
\end{algorithm}

@@

\begin{algorithm}
\setlength\hsize{0.9\linewidth}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{filterByLayer}{filterByLayer}\SetKwFunction{mergeLayers}{mergeLayers}
 \SetKwFunction{eNull}{null}\SetKwFunction{getInputsSatisfied}{getInputsSatisfied}\SetKwFunction{createEdges}{createEdges}
 \LinesNumbered
 \SetNlSty{}{}{:}
 \Input{$start$, $end$, sorted layers $L$, $weights$}
 \Output{final graph $G$}
 $G.nodes \leftarrow \{end\}$\;
 $G.edges \leftarrow \{\}$\;
 $nextToSatisfy \leftarrow \{\}$\;
 \ForAll{$inputs$ of $end$}{
    $nextToSatisfy \leftarrow nextToSatisfy \cup \{(input, end, |L|)\}$\;
 }
 $i \leftarrow |L|$\;
 \For{$i=|L|$ to $i=1$}{
    $toSatisfy \leftarrow \filterByLayer(nextToSatisfy,i)$\;
    $nextToSatisfy \leftarrow nextToSatisfy - toSatisfy$\;
    $mergedL \leftarrow \mergeLayers(L,i)$\;
    \While{$|toSatisfy| > 0$}{
	$nextS \leftarrow mergedL.next()$\;
	\eIf{$nextS = \eNull$}{
	    $nextToSatisfy \leftarrow nextToSatisfy \cup toSatisfy$\;
	    $toSatisfy \leftarrow \{\}$\;
	}{
	    $nLayer \leftarrow nextS.layer$\;
	    $satisfied \leftarrow \getInputsSatisfied(toSatisfy,nextS)$\;
	    \If{$|satisfied| > 0$}{
		$G.nodes \leftarrow G.nodes \cup \{nextS\}$\;
		$G.edges \leftarrow G.edges \cup \createEdges(nextS, satisfied)$\;
		$toSatisfy \leftarrow toSatisfy - satisfied$\;
		\ForAll{$inputs$ of $nextS$}{
		    $nextToSatisfy \leftarrow nextToSatisfy \cup \{(input, nextS, nLayer)\}$\;
		}
	    }
	}
    }
 }
 $G.nodes \leftarrow G.nodes \cup \{start\}$\;
 $G.edges \leftarrow G.edges \cup \createEdges(start,nextToSatisfy)$\;
 \Return $G$\;
\caption{Algorithm for building final graph solution.}
\label{solutionBuilding}
\end{algorithm}
